\include{header.tex}
\begin{document}

%----------Personal Info-----------------
\textbf{\LARGE Hu, Yong-Hao} \\
\vspace{5pt}
\begin{tabular}{l l}
    Address: &\quad No.101, Sweetopia hongo, 6-21-4, Hongo,  \\
             &\quad Bunkyo Ku, Tokyo, 113-0033, Japan\\
    Email:   &\quad yh-haoareyou@g.ecc.u-tokyo.ac.jp\\
    Tel:     &\quad \Plus81\Minus70\Minus2662\Minus6744\\
    Date of birth: &\quad November 11, 1998
\end{tabular}
\vspace{5pt}

%-----------Profile-----------------
\section{Profile}
\vspace{5pt}

    
\vspace{5pt}

%-----------EDUCATION-----------------
\section{Education}
\vspace{5pt}
\resumeSubHeadingListStart
    \resumeSubheading
      {University of Tokyo - Current}{Tokyo}
      {Master of Information Science and Technology}{2022.03 - Expected 2024.03}
    \resumeSubheading
      {Waseda University - Graduated}{Tokyo}
      {Bachelor of Engineering in Computer Science and Engineering}{2017.09 - 2022.03}

\resumeSubHeadingListEnd
\vspace{5pt}

%-----------Work Experience-----------------
\section{Work Experience}
\vspace{5pt}
\resumeSubHeadingListStart
    \resumeSubheading{rooter, Inc.}{Tokyo}
    {Technical Intern}{2019.01 - 2021.01}
    \resumeItemListStart
        \resumeItem{Web Scraping}{Scraping data of advertisements on different SNS and portal sites}
        \resumeItem{Frontend Development}{Using Ruby and Rails and MySQL to visualize crawled data for clients to access and analyze.}
    \resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{5pt}

%-----------Papers-----------------
\section{Conference Appearance}
\vspace{5pt}
\resumeSubHeadingListStart
    \resumeSubheading
        {Improving conversations around controversial issues with Gamification implemented}{}
        {Yong-Hao Hu, Tatsuo Nakajima}{Interaction 2021 (Poster)}
\resumeSubHeadingListEnd
\vspace{5pt}

%-----------Project-----------------
\section{Projects}
\vspace{5pt}
\begin{itemize}[leftmargin=*]
    \item{\textbf{Graduate Thesis - 'Campus' as 'Canvas': General Approach to Revitalize a Place with Location-based Augmented Reality and Co-creation}}
        \begin{itemize}
                \vspace{-5pt}
                \item Developing an AR application where users watch, draw and override AR graffiti at physical locations in campus.
                \item As a proposed method to revitalize general locations with Location-based AR, co-creation and user-user interaction after pandemic.
        \end{itemize}
    \vspace{-10pt}
    \item{\textbf{Current Research - Enhancing Proteus Effect to Improve Avatar User's Sociability}}
        \begin{itemize}
                \vspace{-5pt}
                \item Displaying the process of avatar changing in detail in VR to enhance user's embodiment of the avatar, which further enhances the Proteus effect.
                \item In previous related researches, Proteus Effect's influence on avatar users' behaviors has been confirmed, but the effect were often minor.
        \end{itemize}
    \vspace{-10pt}
    \item{\textbf{Current Lab Project - VR Bike}}
        \begin{itemize}
                \vspace{-5pt}
                \item Having participants ride bicycles in VR and tracking their visual attention to objects with HTC Vive pro eye.
                \item Evaluating the relation between attention and the load of cycling for people with attention deficit.
        \end{itemize}
    \vspace{-10pt}
    \item{\textbf{Open Sources Project - WasedaTime}}
        \begin{itemize}
                \vspace{-5pt}
                \item A free web app featuring timetable, syllabus search, and feeds for Waseda Univ students
                \item Built with ReactJS and micro-frontends framework. https://github.com/wasedatime/wasedatime-web
                \item Working as leader of the development team.
        \end{itemize}
    \vspace{-10pt}
    \item{\textbf{Open Sources Project - Example project for implementation of Vite with single-spa}}
        \begin{itemize}
                \vspace{-5pt}
                \item Proposing a solution to interoperate single-spa, a micro-frontends framework, with Vite, a frontend build tool.
                \item Creating an example demo: https://github.com/YHhaoareyou/vite-single-spa-ts-root-config .
        \end{itemize}
\end{itemize}
\vspace{5pt}

%-----------Skills-----------------
\section{Skills}
\vspace{5pt}
\begin{itemize}[leftmargin=*]
    \resumeSubItem{VR development}{Unity, OpenXR, OpenVR, Oculus SDK}
    \resumeSubItem{AR development}{AR.js, A-frame}
	\resumeSubItem{Web Frontend}{ReactJS, Next.js, Micro-frontends (single-spa), Ruby on Rails, Webpack, Vite, TailwindCSS}
	\resumeSubItem{Mobile App}{React Native}
	\resumeSubItem{Platforms}{Google Firebase, AWS}
	\resumeSubItem{Programming Languages}{JavaScript, TypeScript, C\sharp, Python, Ruby, C, C\Plus\Plus.}
    \resumeSubItem{Communication skills}{Business level in English and Japanese. Fluent in Mandarin. Experiences in academic writing in English.}
\end{itemize}

\end{document}

